\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{longtable}

\definecolor{gain}{RGB}{0,128,0}
\definecolor{loss}{RGB}{200,0,0}
\definecolor{neutral}{RGB}{80,80,80}

\pagestyle{fancy}
\fancyhf{}
\rhead{Allocation Engine --- Internal}
\lhead{Buy Recommendations -- May 2026}
\rfoot{\thepage}

\title{%
  \textbf{Buy Recommendations} -- Trailing 3M + Forward 3M \\[4pt]
  \large Allocation Engine: Current-Market Overlay (May 2026) \\[2pt]
  \normalsize Variance-Kelly framework + post-rotation regime adjustments
}
\author{Allocation Engine Research}
\date{May 7, 2026}

\begin{document}
\maketitle
\thispagestyle{fancy}

% ============================================================
\section{Executive Summary}
% ============================================================

This note translates the allocation-gym Variance-Kelly framework into
concrete buy recommendations for the May--August 2026 window. The
codebase's prior signals (BTC--IWN negative correlation, IWN-put
hedging, quarter-Kelly sizing) are re-overlaid on a market that has
rotated decisively into energy and commodities while small caps and
BTC have given back gains. VIX has collapsed from a March peak of
31.05 to 17.39, making both calls and puts structurally cheap.

\begin{table}[H]
\centering
\caption{Recommended trade book (May 2026)}
\begin{tabular}{l l l l r}
\toprule
Trade & Direction & Tenor & Conviction & Sizing \%NAV \\
\midrule
IWN 3M ATM puts        & \textcolor{loss}{Long Put}  & 3M     & High      & 0.25\% \\
XLY 3M ATM puts        & \textcolor{loss}{Long Put}  & 3M     & Med--High & 0.25\% \\
XLE 3M ATM calls       & \textcolor{gain}{Long Call} & 3M     & High      & 0.40\% \\
IBIT 3M ATM calls      & \textcolor{gain}{Long Call} & 3M     & High      & 0.30\% \\
EWZ 2--3M OTM calls    & \textcolor{gain}{Long Call} & 2--3M  & Med       & 0.20\% \\
DBC 3M ATM calls       & \textcolor{gain}{Long Call} & 3M     & Med       & 0.05\% \\
GLD 3M ATM calls       & \textcolor{gain}{Long Call} & 3M     & Med       & 0.05\% \\
IBIT spot              & \textcolor{neutral}{Long}   & open   & Med       & 30--45\% w/ hedge \\
\bottomrule
\end{tabular}
\end{table}

% ============================================================
\section{Codebase Audit Recap}
% ============================================================

The allocation-gym repository implements a Variance-Kelly backtesting
framework on top of Backtrader. Core analytics include Yang--Zhang
volatility, the Variance Ratio (VR), Efficiency Ratio (ER), regime
classification (CHOP/TREND/MIXED), vol-of-vol, and downside
semivariance. Four strategies are wired in:

\begin{itemize}[nosep]
  \item \textbf{momentum} -- enter when VR $\geq$ 1.1, ER $\geq$ 0.4,
        price $>$ SMA50; exit when price $<$ SMA50 or regime flips to CHOP.
  \item \textbf{mean\_reversion} -- enter when VR $<$ 0.9 and RSI $<$ 30;
        exit when RSI $>$ 70.
  \item \textbf{variance\_kelly} -- Kelly inverse-covariance rebalance,
        with drift $>$ 5\% triggering re-allocation.
  \item \textbf{momentum\_dca} -- Ornstein--Uhlenbeck band selection for
        accumulation.
\end{itemize}

Position sizing uses a quarter-Kelly sizer (0.25 fraction) with
downside-semivariance-derived stop distances. Realised YTD P\&L
(Feb~21 -- Mar~25, 2026) totalled \textcolor{gain}{\textbf{+\$19{,}965}}:
\$15{,}770 from BTC bracket trading on the Grayscale BTC Mini Trust
plus \$4{,}195 from options round-trips.

The codebase's central pair signal is the BTC$\leftrightarrow$IWN 30d
correlation of $+0.61$, with a residual of $+0.28$ after VIX is
controlled for (i.e.\ VIX explains roughly 48\% of the co-movement).
On a cost-of-hedge basis, IWN 3M ATM puts run at 4.4\% of spot versus
15.4\% for BTC puts, a \textbf{3.5$\times$ cheaper hedge} for the same
underlying risk-off scenario.

\subsection{Realised options round-trips}

\begin{table}[H]
\centering
\caption{Closed options round-trips (Feb 21 -- Mar 4, 2026)}
{\small
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r l r r r r}
\toprule
Contract & Qty & Dates & Open & Close & P\&L & Return \\
\midrule
IWN \$262 Put 3/11      & 10 & 02/26 $\to$ 02/27 & \$3.16  & \$4.96  & \textcolor{gain}{+\$1{,}800} & +57\%  \\
IWN \$247 Put 3/13      & 10 & 02/27 $\to$ 03/01 & \$1.41  & \$2.86  & \textcolor{gain}{+\$1{,}450} & +103\% \\
CRWD \$390 Put 3/06     & 1  & 02/25 $\to$ 02/27 & \$21.05 & \$33.30 & \textcolor{gain}{+\$1{,}225} & +58\%  \\
CRWD \$367.5 Put 3/20   & 1  & 02/27 $\to$ 03/04 & \$19.05 & \$16.25 & \textcolor{loss}{--\$280}    & --15\% \\
\midrule
\multicolumn{5}{l}{\textbf{Total Options P\&L}} & \textcolor{gain}{\textbf{+\$4{,}195}} & \\
\bottomrule
\end{tabular*}}
\end{table}

% ============================================================
\section{Current Market State (May 7, 2026)}
% ============================================================

\begin{table}[H]
\centering
\caption{Snapshot of indicators relative to the codebase's prior analysis window}
\begin{tabular}{l r l}
\toprule
Indicator & Value & Move since codebase analysis \\
\midrule
BTC/USD              & \$81{,}022             & \textcolor{loss}{-14\%} from $\sim$\$94K \\
VIX                  & 17.39                  & \textcolor{loss}{-39\%} from March peak 31.05 \\
EWT                  & \$94.41                & \textcolor{gain}{+33\%} in 5 weeks (\$70.77 on Apr 2) \\
EWZ                  & $\sim$\$39             & \textcolor{gain}{+60\%} trailing 1Y \\
S\&P 500 (Q1)        & -4.3\%                 & growth selloff \\
Nasdaq 100 (Q1)      & -5.8\%                 & tech leadership broken \\
XLE Energy (Q1)      & \textcolor{gain}{+37.9\%} & oil +84\%, regime change \\
DBC Commodities (Q1) & \textcolor{gain}{+29.5\%} & rotation winner \\
Russell 2000 (IWM)   & broke Jan ATH          & \textcolor{gain}{+8.6\%} in 2 weeks late Q1 \\
\bottomrule
\end{tabular}
\end{table}

VIX at 31 $\to$ 17 means options are cheap on \emph{both} sides of the
book, which favours long-gamma expressions. The codebase has no
energy or commodity exposure model -- a visible blind spot in the
current rotation, and one this note explicitly patches over via the
XLE / DBC / GLD overlay.

% ============================================================
\section{Trailing 3-Month Review (Feb--May 2026)}
% ============================================================

\begin{itemize}[nosep]
  \item Q1 2026: S\&P -4.3\%, Nasdaq -5.8\%
  \item Sector winners: \textcolor{gain}{XLE +37.9\%} (oil +84\%),
        \textcolor{gain}{DBC +29.5\%}, materials
  \item Sector losers: XLK, XLY, XLF each \textcolor{loss}{$<$-7\%}
  \item Earnings growth divergence: Comm Services +53.2\%, Tech +50.0\%,
        Cons Disc +39.0\%
  \item VIX path: 17 $\to$ 31 (March panic) $\to$ 17 (May complacency)
  \item Russell 2000 broke Jan ATH after \textcolor{gain}{+8.6\%} in
        2 weeks (the ``great rotation'')
  \item BTC drawdown: $\sim$\$94K $\to$ \$81K, \textcolor{loss}{-14\%}
  \item Codebase's IWN puts closed +57\% and +103\% during the March
        vol spike
\end{itemize}

% ============================================================
\section{Forward 3-Month Outlook (May--Aug 2026)}
% ============================================================

\subsection{Catalysts}
\begin{itemize}[nosep]
  \item Powell tenure ends May 2026 $\to$ new (likely dovish) Fed chair
  \item Clarity Act (US crypto regulatory framework) potential vote
  \item 3 Fed cuts on consensus for 2026; June FOMC is the primary marker
  \item \$368B small-cap maturity wall in 2026; Russell 2000 has 32\%
        floating-rate debt vs 6\% S\&P
  \item Geopolitical oil premium persisting
\end{itemize}

\subsection{Consensus price paths}
\begin{itemize}[nosep]
  \item BTC: June high \$83.9K / low \$70.3K, fading to \$71--78K Jul--Aug
  \item IWM: extended at ATH; debt rollover at $\sim$6.5\% structural drag
  \item Energy: momentum intact, no clean reversal
  \item EM equities: EWT parabolic, EWZ has more room
\end{itemize}

% ============================================================
\section{Recommendations}
% ============================================================

\subsection{Call book (forward upside, cheap IV)}

\textbf{XLE 3M ATM calls -- 0.40\% NAV.} Energy is the cleanest
trending regime in the tape: XLE +37.9\% in Q1, oil +84\%, no
catalysts pointing to reversal, and a persistent geopolitical
premium. With VIX at 17 the call is structurally cheap. This is
the highest-conviction long in the book and the largest sizing.

\textbf{IBIT 3M ATM calls -- 0.30\% NAV.} BTC at \$81K against a
consensus June high of \$83.9K plus the Powell-replacement /
Clarity Act catalyst window. Calls are the defined-risk version
of the codebase's BTC long; 3M tenor is sized to capture the June
FOMC and not bleed into the Jul--Aug fade.

\textbf{EWZ 2--3M OTM calls -- 0.20\% NAV.} Brazil is the EM beta
that still has room: +60\% trailing 1Y, riding commodity and
supply-chain tailwinds, and not yet parabolic in the way EWT is.
OTM strikes give convex payoff if the commodity rotation persists.

\textbf{DBC 3M ATM calls -- 0.05\% NAV.} Token sizing on the broad
commodity basket as a co-trade with XLE; DBC +29.5\% in Q1 keeps
it the cleanest portfolio expression of the rotation.

\textbf{GLD 3M ATM calls -- 0.05\% NAV.} Token sizing on gold as a
dovish-Fed / weaker-USD beneficiary; sits naturally alongside the
DBC sleeve and hedges the call book against a stagflation tail
where rates fall but growth disappoints.

\subsection{Put book (forward downside, structural)}

\textbf{IWN 3M ATM puts -- 0.25\% NAV.} The codebase's flagship
hedge: IWN puts closed +57\% and +103\% during the March vol
spike. Russell 2000 is extended at ATH, carries 32\% floating-rate
debt, and faces the \$368B small-cap maturity wall through 2026.
At 4.4\% of spot vs 15.4\% for BTC puts, it remains a 3.5$\times$
cheaper expression of the same risk-off scenario.

\textbf{XLY 3M ATM puts -- 0.25\% NAV.} Consumer discretionary is
already a Q1 loser ($<$-7\%) yet still trades on consumer-strength
narrative; if the rate-cut path delays or earnings deceleration
broadens, XLY is the cleanest single-sector short. Sized equal to
IWN puts to diversify the put book across small-cap-debt and
consumer-spend factors.

\subsection{Pair trade -- modernized codebase pair}

\begin{enumerate}[nosep]
  \item \textbf{Long XLE 3M calls + Long IWN 3M puts.} Both legs
        monetize the stagflation / oil-spike / small-cap-debt-wall
        scenario; positively skewed, and patches the codebase's
        energy blind spot.
  \item \textbf{Long IBIT 3M calls + Long IWN 3M puts.} Preserves
        the structural BTC-vs-small-cap pair the codebase
        identified, but with a defined-risk BTC long via IBIT
        calls instead of GBTC spot.
\end{enumerate}

\subsection{Avoid (or trim if held)}
\begin{itemize}[nosep]
  \item EWT calls (parabolic +33\% in 5 weeks)
  \item XLK / QQQ calls (no catalyst)
  \item RBC (+120\% 1Y, codebase short-thesis candidate, trim)
  \item BTC calls past 3M tenor (Jul--Aug fades)
\end{itemize}

% ============================================================
\section{Universe -- Codebase Reference Tables}
% ============================================================

\subsection{Top 10 BTC-LONG thesis (negative BTC correlation)}

\begin{longtable}{l l r r r r r}
\toprule
Rank & Ticker & Spot & 30d Vol & 3M Corr & 1Y Return & Score \\
\midrule
\endhead
1  & WEAT  & \$21.99   & 23.0\% & -0.333 & -16.7\%                 & 0.523 \\
2  & EWZ   & \$38.64   & 27.1\% & -0.253 & \textcolor{gain}{+33.5\%} & 0.495 \\
3  & EWT   & \$75.07   & 24.0\% & -0.257 & \textcolor{gain}{+71.5\%} & 0.479 \\
4  & XLY   & \$115.42  & 16.4\% & -0.269 & \textcolor{gain}{+28.6\%} & 0.479 \\
5  & EEM   & \$61.50   & 18.5\% & -0.212 & \textcolor{gain}{+59.7\%} & 0.473 \\
6  & MOO   & \$85.20   & 14.2\% & -0.198 & \textcolor{gain}{+25.4\%} & 0.469 \\
7  & REXR  & \$37.65   & 28.3\% & -0.233 & -22.6\%                 & 0.469 \\
8  & HYG   & \$80.28   & 2.6\%  & -0.201 & \textcolor{gain}{+16.4\%} & 0.455 \\
9  & VWO   & \$57.24   & 15.1\% & -0.165 & \textcolor{gain}{+46.8\%} & 0.454 \\
10 & SOYB  & \$23.69   & 9.3\%  & -0.167 & -2.7\%                  & 0.450 \\
\bottomrule
\end{longtable}

\subsection{Top 10 BTC-SHORT thesis (positive BTC correlation)}

\begin{longtable}{l l r r r r r}
\toprule
Rank & Ticker & Spot & 30d Vol & 3M Corr & 1Y Return & Score \\
\midrule
\endhead
1  & GMED  & \$93.80   & 23.7\% & +0.154 & \textcolor{gain}{+69.9\%}  & 0.436 \\
2  & RJF   & \$154.42  & 35.9\% & +0.158 & \textcolor{gain}{+31.3\%}  & 0.434 \\
3  & MIDD  & \$164.99  & 29.4\% & +0.139 & \textcolor{gain}{+7.1\%}   & 0.424 \\
4  & PODD  & \$245.45  & 32.7\% & +0.099 & \textcolor{gain}{+46.3\%}  & 0.421 \\
5  & CFLT  & \$30.70   & 3.3\%  & +0.128 & -11.1\%                  & 0.416 \\
6  & RBC   & \$584.89  & 18.7\% & +0.042 & \textcolor{gain}{+120.1\%} & 0.415 \\
7  & URBN  & \$65.69   & 35.9\% & +0.089 & \textcolor{gain}{+52.4\%}  & 0.413 \\
8  & WES   & \$42.09   & 22.9\% & +0.136 & \textcolor{gain}{+49.3\%}  & 0.412 \\
9  & IWO   & \$338.51  & 21.3\% & +0.049 & \textcolor{gain}{+27.7\%}  & 0.404 \\
10 & GGG   & \$94.82   & 18.8\% & +0.040 & \textcolor{gain}{+6.3\%}   & 0.401 \\
\bottomrule
\end{longtable}

% ============================================================
\section{Caveats and Known Risks}
% ============================================================

\begin{itemize}[nosep]
  \item Codebase data is $\sim$60 days stale; correlations may have
        shifted in the post-VIX-collapse risk-on regime
  \item Codebase has no energy/commodity exposure model -- XLE/DBC/oil
        are blind spots
  \item EWT was the codebase's \#3 negative-corr trade -- now too
        extended; do not conflate prior signal with current entry
  \item Calls + puts at low IV = long-gamma straddle book; theta
        bleed if vol stays pinned at 17
  \item June FOMC + Powell-replacement is the single biggest 3M
        risk-event -- time expiries through it
  \item Variance-Kelly's quarter-Kelly is sized for trending regimes;
        chop will degrade Sharpe
\end{itemize}

% ============================================================
\section{References}
% ============================================================

\begin{itemize}[nosep]
  \item \href{https://fortune.com/article/price-of-bitcoin-05-07-2026/}{Bitcoin price May 7, 2026 -- Fortune}
  \item \href{https://seekingalpha.com/article/4887991-q1-2026-recap}{Q1 2026 Recap -- Seeking Alpha}
  \item \href{https://markets.financialcontent.com/stocks/article/marketminute-2026-3-11-the-great-rotation-russell-2000-surges-89-as-small-cap-value-dethrones-tech-giants-in-2026}{Russell 2000 surges 8.9\% -- FinancialContent}
  \item \href{https://markets.financialcontent.com/stocks/article/marketminute-2026-3-23-small-caps-under-siege-russell-2000-enters-correction-as-yields-surge}{Small caps under siege -- FinancialContent}
  \item \href{https://changelly.com/blog/bitcoin-price-prediction/}{Bitcoin price predictions 2026 -- Changelly}
  \item \href{https://stockanalysis.com/etf/ewt/}{EWT Stock Analysis -- stockanalysis.com}
  \item \href{https://247wallst.com/investing/2026/05/01/the-cboe-vix-falls-to-16-level-as-risk-on-trade-returns-to-market/}{VIX falls below 17 -- 24/7 Wall St.}
  \item \href{https://247wallst.com/investing/2026/05/07/how-ewz-and-eww-investors-are-riding-commodity-and-supply-chain-tailwinds/}{EWZ commodity tailwinds -- 24/7 Wall St.}
\end{itemize}

\end{document}
